% BEGINNING OF COMMENT
%
% This is a section for you to write your introduction to your personal letter. Please note that you need to add two backslashes // to properly make the indentation work. I could solve it with code but can't be bothered.
%
% END OF COMMENT

\documentclass[../main.tex]{subfiles}
\begin{document}
\par
In August 2020, I moved to Stockholm to study Electronics and Computer Science at KTH. During the first year of my studies, I worked as a freelancer, part-time, helping clients to modernize their brands. I did this mainly through web, logo, and marketing designs.
\\

During the summer of 2021, I got a full-time internship for AWS maintaining their servers in Eskilstuna. It has allowed me to learn and grow about server hardware, networking, virtualization, operating systems, and the cloud industry.
\\

This internship gave me the interest and knowledge that I needed to start exploring with Linux and server software on my free time. After going down the rabbit-hole of "homelab" technologies such as Proxmox, Networking, Raspberry pis, etc; I got the experience I needed to fully self host my own services. As of today I am self hosting my own router, git server, media server, password manager, cloud storage (nextcloud), and reverse proxy (nginx). All this on three machines to build a high availability cluster using Docker, Ansible, and Kubernetes, to back up all my data, which is all documented on "homelab" github repository.
\\

On top of this I often work on my own website, calexanderberg.com, on my free time. I recently rewrote in plain HTML as I found it hard to constantly update my web development websites as information turned irrelevant or as I found the design boring. I have written my website in multiple frameworks in the past, React, Vue, Rust/Webassemblys, etc. I also have a blog that is written in Zola that I use to write about technology and philosophy, the link to this is on my website.
\\

Since my internship I worked briefly as an electronic system support agent at SEB before I worked as a QA test analyst at Nasdaq. I was hired to help write and create automation scripts for Nasdaq's internal system in the European markets. This allowed me to work with technologies like Pandas, Playwright, and Robot framework, just to name a few. This job has given me much more experience with Git, GitLab, CI/CL, WSL, and overall how big projects are managed between multiple team members. We also use Agile and scrum in our workflow helping us manage issues over extended periods of time. I left Nasdaq in late 2023 to be able to focus on finishing my studies.
\\

\end{document}
