% BEGINNING OF COMMENT
%
% This is a section for you to write your projects, it is identical to the education section. Add all your experience and certificates that you feel is relevant to your job.
%
% END OF COMMENT

\documentclass[../main.tex]{subfiles}
\begin{document}

\project
    {Bug-Tracker}
    {November 2021 - January 2022}
    {Built a jira-like app with a team as part of a competition within my web development course. We used the github API to connect it to excisting github projects and allowed all tickets to be directly connected to issues. We won the competition and were rewarded with honors.}
    {Firebase, NodeJS, React, Javascript/Typescript, API, Model-View-Controller}

\project
    {Homelab}
    {October 2021 -}
    {A collection of the services I self-host and my experience with backend technologies like NGINX, Linux, Docker, etc. As well as overall networking like reverse proxy, SSL, Load balancing, etc. This includes my website calexanderberg.com. Feel free to give me a visit.}
    {Reverse proxy, SSL, Docker, Kubernetes, Sysadmin, Networking, NGINX, Linux}


\project
    {Business Verification Automation Tools, BVAT}
    {June 2023 - July 2023}
    {My project to standardize the tools used in my team, Business Verification, at Nasdaq. This includes a universal docker image for our tests, using Cypress, Playwright, and Robot Framework, and a universal node modules folder using git submodules. This had to be implemented and tested for each project for the entire team.}
    {Docker, Agile, GitLab Ci/CD, NodeJS}
    
\end{document}