% BEGINNING OF COMMENT
%
% Personal section for a personal letter. This is usually the only thing I add to my resume
%
% END OF COMMENT

\documentclass[../../main.tex]{subfiles}
\begin{document}

I hope I have shown that I have a deep interest in devops, software engineering, and the tech stack in general. I would love to use my current experience to build hardware and software that connectes the world forward. I am personally very interested in low level computation and hardware, or how to make our day to day systems more efficient. An example of this is my thesis topic that was just approved which will focus on the instructions used by a low level AI framework (Tinygrad) in order to give a loose guide to write a DSP AI accelerator for said AI framework.


As a person who works in mulitple environments I find myself using the app Spotify has for the web, IOS, Linux, Mac, and windows. If I am going to be honest there are plenty of differences between these apps (such as short pauses between songs on the web, or audio and video being out of sync on podcasts which are speed up), this makes me want to focus on QA testing using my experience from Nasdaq. On top of this I also have a collection of Vinyls and listening to files with lossless and lossy compression, makes me wonder if it would be possible to use my backend and devops experience to improve the streaming quality from Spotify.

Long story short I am a massive fan of Spotify's ecosystem and want to improve it in any way I can, to help build the future of music.
\\
\end{document}
